%\input{head.tex}

%\begin{document}



\section{Basic Concepts}

Most of the following concepts apply to arbitrary groups.

\subsection{Groups and Subgroups}

\defn{
group, Abelian, conjugate, power, finite, cyclic, subgroup, generate, order, complex product, coset, coset, transversal, p-group. 
}

\prop{
bijective mappings, cyclic groups, subgroup, set-generate, complex product, order of c.p., Lagrange Thm, order of g and G, transversal, complement, Dedekind Identity. 
}

\subsection{Homomorphisms and Normal Subgroups}

\defn{
homomorphism, im, ker, epi/mono/endo/iso/automorphism, normal, simple, factor group, subnormal, section. 
}

\prop{
inverse homo, ker is normal, normal iff, natural homo, Homo Thm, Iso Thm*2, subnormal.
}

\subsection{Automorphisms}

\defn{
AutG, InnG, Z(G), characteristic, X-inv, X-homo. 
}

\prop{
cyclic G/Z(G) implies Abelian G, char is trans. 
}

\subsection{Cyclic Groups}

\defn{$C_n$}

\prop{
subgroups of $\Z$, finite cyclic groups and their subgroups, char, cyclic p-groups, Abelian simple groups. 
}

\subsection{Commutators}

\defn{
commutator subgroup, perfect. 
}

\prop{
comu with homo, smallest s.t. Abelian factor, perfect factor, $[x,yz]=[x,z][x,y]^z$, [X,Y] is normal in $<X,Y>$, Three-subgroups Lem. 
}

\subsection{Products of Groups}

\defn{
internal/external direct product, central product, internal/external semidirect product, involutions, dihedral group. 
}

\prop{
in/ex iso, on Z(G) G' G/N, on normal N, internal structures $G/\bigcap_i N_i \cong G/N_1\times\cdots\times G/N_n$, prod of normal subgs of relative prime order is direct, on elements, central product on G/Z[G], factorization and product of elements in a semiderict product, dihedral groups are semidirect products. 
}

\subsection{Minimal Normal Subgroups}

\defn{
minimal normal subgroups. 
}

\prop{
properties of a min-normal subg, product of min-normal subgs, factorization(structure for Abelian versus uniqueness for non-Abelian). 
}

\subsection{Composition Series}

\defn{
refine normal(rep. subnormal)series to chief(esp. composition) series, solvable group, X-section, X-composition series, X-simple. 
}

\prop{
Jordan-Holder Thm. 
}


%%%%%%%%%% below are solutions of exercises %%%%%%%%

\begin{exerlist}

\exer{hahaha}{jajaja}
	
\end{exerlist}




%\end{document}